---
title: "Draft History"
author: "Tom Kain"
date: "July 2, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
```

Importing draft results in their varying format from 2011-2018
```{r import}
drafts_old_raw <- here("data", "2011-2015_draftResults.csv") %>% 
  read_csv() %>% 
  clean_names()

draft_2016_raw <- here("data", "2016_draftResults.csv") %>% 
  read_csv() %>% 
  clean_names()

draft_2017_raw <- here("data", "2017_draftResults.csv") %>% 
  read_csv() %>% 
  clean_names()

draft_2018_raw <- here("data", "2018_draftResults.csv") %>% 
  read_csv() %>% 
  clean_names()
```

Columns I want in the final data set:

1. Year 
2. Player name
3. Position
4. Projected Tier (1 = best)
5. Draft Team
6. Draft Price

Maybe later worry about joining with some then-projected value. Some things to clean up:

1. Player name convention (First name vs initial)
2. Convert ADP to Tier
3. Probably drop Kickers, maybe DEF too
4. Verify price is numeric (integer)

```{r clean_old_drafts}
draft_2015 <- drafts_old_raw %>% 
  filter(year == 2015) %>% 
  select(-pick) %>% 
  mutate(price = price %>% str_sub(2) %>% as.numeric)

draft_2015 %>% 
  filter(!is.na(adp)) %>% 
  ggplot(aes(adp, position, color=position)) +
  geom_point() 

draft_2017_raw %>% 
  filter(!is.na(spent)) %>% 
  mutate(tier = as_factor(tier),
         spent = spent %>% str_sub(2) %>% as.numeric) %>% 
  ggplot(aes(spent, position, color=tier)) +
  geom_point() +
  scale_x_reverse()

draft_
```